Empirical Bayes analysis for detection of gene heterosis in RNAseq data

### 2014-12-22 ebayes_rnaseq_heterosis.tex
Added comments to model section.

We assume improper uniform priors for $\eta$ and take $\tau\stackrel{ind}{\sim} Ca^+(0,3)$, where 0 and 3 are the location and scale parameters, respectively, of the untruncated half-Cauchy distribution. In the independent model, we also assign the $Ca^+(0,3)$ prior to the diagonal elements of $\Sigma$. In the covariance model, we assume a conjugate, proper inverse Wishart distribution with degrees of freedom $V+2$ and an identity scale matrix, resulting in marginally uniform correlations.

>>>>

We assume improper uniform priors for $\eta$ and take 
%In fact, the prior on \tau is just Unif(0,5)
$\tau\stackrel{ind}{\sim} Ca^+(0,3)$, where 0 and 3 are the location and scale parameters, respectively, of the untruncated half-Cauchy distribution. In the independent model, we also assign the $Ca^+(0,3)$ prior to the
diagonal elements
%square root of diagonal elements?
of $\Sigma$. In the covariance model, we assume a conjugate, proper inverse Wishart distribution with degrees of freedom $V+2$ and an identity scale matrix, resulting in marginally uniform correlations.
